### 2020-11-22 manuscript/manuscript.rmd
more on formats

---
bibliography: manuscript.bib
csl: nature.csl
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
  word_document: default
  github_document: default
---

@@

@@

## Main

@@

## Supplementary materials

@@

## Supplementary Information

### S.1 Summaries of published analyses

@@

### S.2 Models of molecular evolution

@@

### S.3 Data-recoding methods

>>>>

---
bibliography: manuscript.bib
csl: science.csl
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output:
  html_document: default
  pdf_document:
    latex_engine: xelatex
  word_document: default
  github_document: default
---

@@

**Short title:** Rooting the animal tree of life

**One sentence Summary**: We explore the root of animal tree by synthesizing past work, perform new phylogenomic and sensitivity analyses, and found that the primary source of variation between results is the number of categories used in site-heterogeneous models.

@@

## Main Text

@@

## List of Supplementary materials
Materials and methods
Table S1 - S8
Fig. S1 - S9
Supplementary text S1 - S3

## Supplementary Materials

@@

## Supplementary text

### S1 Summaries of published analyses

@@

### S2 Models of molecular evolution

@@

### S3 Data-recoding methods
